Report

### 2022-04-07 Analysis/Report.Rmd
minor commit

---
title: "Report"
author: "Eli Clapper"
date: "23/03/2022"
output: html_document
---

@@

<!--
call library and load in results. The `dat` `data.table` is subsetted for all cases where $es >= .1$ . This removes 108/3 = 36 conditions from the results.
-->
```{r, echo = F}
library(data.table) # load in libraries
library(DT)
library(ggplot2)
dat <- readRDS(file.path("Sim_Eli", "sim_results_2022-03-19.RData")) #
dat <- dat[!es < .1]
```

>>>>

---
title: "Report"
author: "Eli Clapper"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

<!--
call library and load in results. The `dat` `data.table` is subsetted for all cases where $es >= .1$ . This removes 108/3 = 36 conditions from the results.
-->

```{r, echo = F}
library(data.table) # load in libraries
library(DT)
library(ggplot2)
dat <- readRDS(file.path("../Sim_Eli", "sim_results_2022-03-19.RData")) #
dat <- dat[!es < .1]
```
